The CMS Data Aggregation System

### 2010-05-04 doc/paper.tex
Added ATLAS AMI web portal reference for completeness
git-svn-id: svn+ssh://svn.cern.ch/reps/CMSDMWM/DAS/trunk@557 4525493e-7705-40b1-a816-d608a930855b

\section{Related Work\label{RelatedWork}}
Even though the idea of querying relation databases via keyword based search
algorithms is not knew it is still under significant activity in computer
science domain. A few alternative solutions has been proposed to address this issue
in last several years. The federated DB \cite{FedDB} by IBM unifies data coming 
from different RDMS into another DB where SQL queries can be placed to search desired
data. The other approaches \cite{DBXplorer, QueryAnswer}, influenced by great success
of search engines, explored ability to use keyword search algorithms over relataional RDMS
by indexing DB content. In former case, you still face a problem with understanding 
of underlying schema and imposing relational conditions in your query, while 
in later queries can be expressed via simple keyword based search, even though exact match
of provided keywords is expected. Although keyword based search is
intuitive and easy to use, with respect to HEP and other domains it is not sufficient. 
For example, it does provide provide ability to place conditions expressions between
keys (DB entities/attributes) and their values. The proximity of results becomes very poor
or impossible in case of numbers, aggregate functions, etc. To address this issues
an attempt to build a simple, intuitive and flexible query language was introduced
in \cite{DBS-QL}. It represented a power of SQL while
hiding underlying relational schema from the end users. As a results
a human questions were intuitively mapped into simple queries. For example,
the question
{\it I'm looking for files who contain data taken on certain date and located at
particular site} was represented as simple as
\begin{verbatim}
find file where date 2009-01-02 11:59 CET and site = T2
\end{verbatim}
We wanted to expand this approach to handle broad variety of relational and
non-relational data-sources in CMS within our distributed heterogeneous environment.
At the same time we wanted to simplify it up to the level that users will be
able to place free text-based queries (keyword based search) to look-up their desired data.

@@

>>>>

\section{Related Work\label{RelatedWork}}
Even though the idea of querying relation databases via keyword based search
algorithms is not knew it is still under significant activity in computer
science domain. A few alternative solutions has been proposed to address this issue
in last several years. The federated DB \cite{FedDB} by IBM unifies data coming 
from different RDMS into another DB where SQL queries can be placed to search desired
data. The other approaches \cite{DBXplorer, QueryAnswer}, influenced by great success
of search engines, explored ability to use keyword search algorithms over relataional RDMS
by indexing DB content. In former case, you still face a problem with understanding 
of underlying schema and imposing relational conditions in your query, while 
in later queries can be expressed via simple keyword based search, even though exact match
of provided keywords is expected. Although keyword based search is
intuitive and easy to use, with respect to HEP and other domains it is not sufficient. 
For example, it does provide provide ability to place conditions expressions between
keys (DB entities/attributes) and their values. The proximity of results becomes very poor
or impossible in case of numbers, aggregate functions, etc. To address this issues
an attempt to build a simple, intuitive and flexible query language was introduced
in \cite{DBS-QL}.\footnote{The ATLAS experiment at CERN, has been developed
AMI web portal \cite{AMI} with similar functionality.}
It represented a power of SQL while
hiding underlying relational schema from the end users. As a results
a human questions were intuitively mapped into simple queries. For example,
the question
{\it I'm looking for files who contain data taken on certain date and located at
particular site} was represented as simple as
\begin{verbatim}
find file where date 2009-01-02 11:59 CET and site = T2
\end{verbatim}
We wanted to expand this approach to handle broad variety of relational and
non-relational data-sources in CMS within our distributed heterogeneous environment.
At the same time we wanted to simplify it up to the level that users will be
able to place free text-based queries (keyword based search) to look-up their desired data.

@@

\bibitem{AMI}
Altas AMI web portal:
http://ami.in2p3.fr/opencms/opencms/AMI/www/Tutorial/AMIMediation.html
